MacLeish

### 2021-08-06 README.Rmd
More URL fixes

This R package allows you to download and process weather data using the [ETL](https://www.github.com/beanumber/etl) framework from the MacLeish Field Station. It also contains shapefiles for contextualizing spatial information.

@@

Weather readings are logged every 10 minutes. Current and historical (dating back to 1/3/2012 for `whately` and 6/27/2014 for `orchard`) meteorological readings are available through the [ETL](https://www.github.com/beanumber/etl) framework. Please see the documentation for that package for more information about how this works.

@@

- [Ada and Archibald MacLeish Field Station](https://www.smith.edu/about-smith/sustainable-smith/macleish)
- **[etl](https://www.github.com/beanumber/etl)**

>>>>

This R package allows you to download and process weather data using the [ETL](https://github.com/beanumber/etl) framework from the MacLeish Field Station. It also contains shapefiles for contextualizing spatial information.

@@

Weather readings are logged every 10 minutes. Current and historical (dating back to 1/3/2012 for `whately` and 6/27/2014 for `orchard`) meteorological readings are available through the [ETL](https://github.com/beanumber/etl) framework. Please see the documentation for that package for more information about how this works.

@@

- [Ada and Archibald MacLeish Field Station](https://www.smith.edu/about-smith/sustainable-smith/macleish)
- **[etl](https://github.com/beanumber/etl)**
